Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-31 paper.tex
Re sensitivity

We expect that lower lift on the blades at lower $Re$ will weaken tip vortex
shedding, and decrease the levels of turbulence shed from the blade boundary
layers. As mentioned previously, the dynamic stall vortex shedding is not
expected to have a large Reynolds number sensitivity, though a larger separation
bubble at lower $Re$ may induce higher levels of turbulence as shed vortices
become unstable and break down.

>>>>

We expect that lower lift on the blades at lower $Re$ will weaken tip vortex
shedding, and decrease the levels of turbulence shed from the blade boundary
layers. As mentioned previously, the dynamic stall vortex shedding is not
expected to be highly sensitive to Reynolds number, though a larger separation
bubble at lower $Re$ may induce higher levels of turbulence as shed vortices
become unstable and break down.
